### 2018-10-22 ANA-TOPQ-2017-07-PAPER-auxmat.tex
updating captions of ranking plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.eps} \\
\caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
the case of the $\Hc$ search.
Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
ordered by its impact on $\mu$.} 
\label{fig:ranking_bb}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.eps} \\
\caption{$\Htautau$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
the case of the $\Hc$ search.
Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
For experimental uncertainties that are decomposed into several independent sources, NP I and NP II correspond to the first and second nuisance parameters, 
ordered by its impact on $\mu$.} 
\label{fig:ranking_tautau}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.eps} \\
\caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
the case of the $\Hc$ search.
Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
The parameter $\mathrm{k}(\ttbin)$ refers to the floating normalisation of the $\ttbin$ background, for which the pre-fit impact on $\mu$ is not defined, 
and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
ordered by its impact on $\mu$.} 
\label{fig:ranking_bb}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.eps} \\
\caption{$\Htautau$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
the case of the $\Hc$ search.
Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
The parameter $\mathrm{k}($Fake $\had)$ refers to the floating normalisation of the fake $\had$ background, for which the pre-fit impact on $\mu$ is not defined, 
and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
For experimental uncertainties that are decomposed into several independent sources, NP I and NP II correspond to the first and second nuisance parameters, 
ordered by its impact on $\mu$.} 
\label{fig:ranking_tautau}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
